Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-29 paper.tex
update

\section{Related Work} \label{relatedWork}
Substantial works on web service composition focus on either semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive}, However, only a few researchers address both semantic matchmaking quality and QoS requirements for web service composition problems. To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some attempts on service composition that considers both aspects.

@@

QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques for finding near-optimised solutions. Qi et al. \cite{qi2010combining} propose a heuristic service composition method, named LOEM (Local Optimisation and Enumeration Method), where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal QoS. However, there exists a scalability problem for the enumeration technique. EC techniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problem. Gupta et al. \cite{gupta2015optimization} employ a modified Genetic Algorithm (GA) using a binary string as an individual, which demands to be decoded into composition solutions. Genetic Programming (GP) are used by \cite{yu2013adaptive} to find optimal solutions, which is reached by penalising infeasible solutions using a fitness function. A hybrid approach employs both greedy search algorithm and GP introduced in \cite{ma2015hybrid} to generate solutions that are functionally correct. In particularly, greedy search techniques have been used to generate directed acyclic graphs (DAGs) as composition solutions that is further transferred to tree structures for initialisation and mutation. To eliminating the transformation process from DAGs, a promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation. An indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as an indirect representation that is decoded into a DAG-based solution. These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality, which could lead to too specific outputs produced by the selected services, and this finding is supported by our first comparison experiment.

Only a few works \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} consider both semantic matchmaking quality and QoS simultaneously. Lecue et al. \cite{lecue2009optimizing} propose a semi-automated web service composition using GA to encode a given abstract service workflow, where the semantic matchmaking quality is measured through evaluating the quality of semantic links that require a complete and formal definition of ontology in Description Logic. This evaluation model takes huge cost and time for the domain experts to establish required ontology. Another GA-based approach \cite{fanjiang2014semantic} utilise process description language to encode pre-stored cases-based workflows, where workable services are composed to complete this workflow. The work \cite{pop2009immune} is an automated immune-inspired web service composition approach, where an indirect representation that a binary alphabet is used to encode a planning graph. However, this composition method is only evaluated on a set of scenarios.

In summary, despite a large number of approaches for semantic web service composition and QoS-aware service composition approaches, there is a lack of a fully automated semantic web service composition approach to optimise semantic matchmaking quality and QoS simultaneously, and this approach must be tested utilising benchmark dataset. Therefore, we first propose a general comprehensive quality model that aims to achieve a better semantic matchmaking quality with a slight trade-off in QoS, and then we propose an automated PSO-based approach with explicit support for the comprehensive model to find optimal service compositions.

@@

Our comprehensive quality evaluation model is considered to be more general. Two semantic matchmaking types (Exact and Plugin) are considered for discovering desired web service in recent QoS-aware web service composition  \cite{ma2015hybrid,da2016particle,da2015graphevol}, but there are no measurements of matchmaking types and concept similarities in their approaches. Consequently, weights for $MT$ and $S$ are considered to be 0 in our proposed comprehensive evaluation model, it turns to be a widely used QoS evaluation model in \cite{ma2015hybrid,da2016particle,da2015graphevol}.

>>>>

\section{Related Work} \label{relatedWork}
Substantial works on web service composition focus on either semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,ma2015hybrid,qi2010combining,da2016particle,da2015graphevol,yu2013adaptive}, However, only a few researchers address both semantic matchmaking quality and QoS requirements for web service composition problems. To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some attempts on service composition that considers both aspects.

@@

QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques for finding near-optimised solutions. Qi et al. \cite{qi2010combining} propose a heuristic service composition method, named LOEM (Local Optimisation and Enumeration Method), where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near optimal QoS. EC techniques are used to automatically generate solutions with optimal QoS. Gupta et al. \cite{gupta2015optimization} employ a modified Genetic Algorithm (GA) using a binary string as an individual, which demands to be decoded into composition solutions. Genetic Programming (GP) are used by Yu et al. \cite{yu2013adaptive}, the optimal solutions are reached by penalising infeasible solutions using a fitness function. A hybrid approach employing a greedy search and GP is introduced in \cite{ma2015hybrid} to generate functionally correct tree-based individuals, which are transformed from DAGs. To eliminating the transformation process, a promising GraphEvol is proposed in \cite{da2015graphevol}, where DAG-based service composition representations employ Graph-based evolutionary operators. An indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as an indirect representation that is decoded into a DAG. These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality, which could lead to too specific outputs produced by the selected services.

Only a few works \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} consider both semantic matchmaking quality and QoS simultaneously. Lecue et al. \cite{lecue2009optimizing} propose a semi-automated web service composition using GA to encode a given abstract service workflow, where the evaluation of semantic matchmaking quality requires a complete and formal definition of ontology using description logic that associated to the resources of web services. Another GA-based approach \cite{fanjiang2014semantic} utilise process description language to encode pre-stored cases-based workflows, where workable services are composed to complete this workflow. An automated immune-inspired web service composition approach \cite{pop2009immune} employs a clonal section algorithm with an decoded planning graph, but this approach is only studied in some cases.

In summary, despite a large number of approaches for semantic web service composition and QoS-aware service composition approaches, there is a lack of a fully automated semantic web service composition approach to optimise semantic matchmaking quality and QoS simultaneously. Therefore, we first propose an automated comprehensive quality-aware semantic web service composition approach. To do that, we will design a comprehensive quality model that considers both QoS and quality of semantic matchmaking between services. We will then propose a PSO-based approach to this semantic service composition using our proposed comprehensive quality model to evaluate candidate solutions.

@@

Our comprehensive quality evaluation model is considered to be more general. Two semantic matchmaking types (Exact and Plugin) are considered for discovering web services in recent QoS-aware web service composition  \cite{ma2015hybrid,da2016particle,da2015graphevol}, but there are no measurements of semantic matchmaking quality in their approaches. Consequently, weights for $MT$ and $S$ are considered to be 0 in our proposed comprehensive evaluation model, it turns to be a widely used QoS evaluation model in \cite{ma2015hybrid,da2016particle,da2015graphevol}.
